Trilemma

### 2022-09-27 Trilemma_clustering.Rmd
subnational analysis of SDG + back ups

```{r}
ecofp <- list()
fls <- list.files("data/ecofootprint/")
ecofp <- map(fls, function(x) {
    jsonlite::read_json(
        path = paste0("data/ecofootprint/", x),
        simplifyVector = TRUE)
    }) %>% 
    bind_rows()

@@

# ggsave(
#     plot = p, path = "figures/", file = "first_diff.png", device = "png",
#     width = 6, height = 3, dpi = 300, bg = "white")
p + theme_light(base_size = 20)
```
```{r fig.width=3, fig.height=3}
c1 <- df_dat |> 
    ggplot(aes(EFconsPerCap, gini)) +
    geom_hline(yintercept = 30, linetype = 2, color = "gray50") +
    geom_vline(xintercept = 1.68, linetype = 2, color = "gray50") +
    geom_density2d(size = 0.25, color = "#446B9C") +
    geom_point(aes(color = gni_log), size = 0.5) +
    geom_path(aes(group = country), size = 0.1) +
    scico::scale_color_scico("GNI [log]") +
    labs(y = "Gini", x = "Ecological footprint") +
    theme_light(base_size = 6) +
    theme(legend.position = "top", panel.grid = element_blank(),
          legend.key.width = unit(7, "mm"), legend.key.height = unit(2,"mm"))

c1 + theme_light(base_size = 18)
```
```{r fig.width=3, fig.height=3}
c2 <- df_dat |> 
    ggplot(aes(gni2, gini)) +
    geom_density2d(size = 0.25, color = "#446B9C") +
    geom_point(aes(color = EFconsPerCap), size = 0.5) +
    geom_path(aes(group = country), size = 0.1) +
    geom_hline(yintercept = 30, linetype = 2, color = "gray50") +
    geom_vline(xintercept = (12546), linetype = 2, color = "gray50") +
    scico::scale_color_scico("Ecological footprint",palette = "berlin") +
    labs(x= "GNI [log]", y = "Gini") +
    scale_x_log10() +
    theme_light(base_size = 6) +
    theme(legend.position = "top", panel.grid = element_blank(),
          legend.key.width = unit(7, "mm"), legend.key.height = unit(3,"mm"))

c2 + theme_light(base_size = 7)
```
```{r fig.width=3, fig.height=3}
c3 <- df_dat |> 
    ggplot(aes(gni2, EFconsPerCap)) +
    geom_density2d(size = 0.25, color = "#446B9C") +
    geom_point(aes(color = gini), size =0.5) +
    geom_path(aes(group = country), size = 0.1) +
    scico::scale_color_scico("Gini") +
    labs(x = "GNI", y = "Ecological footprint") +
    scale_x_log10()+
    geom_hline(yintercept = 1.68, linetype = 2, color = "gray50") +
    geom_vline(xintercept = (12546), linetype = 2, color = "gray50") +
    theme_light(base_size = 6) +
    theme(legend.position = "top", panel.grid = element_blank(),
          legend.key.width = unit(7, "mm"), legend.key.height = unit(3,"mm"))

@@

pc1 <- ggbiplot::ggbiplot(
    pc, groups = as.character(stab@clusterObjs$kmeans$`3`$cluster),
    ellipse = TRUE, labels = df_summary$country_code, labels.size = 1.5,
    varname.size = 2) +
    scale_color_manual("Groups", values = c("#73B3A3","#FEA621","#5BA4CA")) +
    labs(tag = "A") +
    theme_light(base_size = 6) +
    theme(legend.position = c(0.2, 0.2), panel.grid = element_blank(),
          legend.text = element_text(size = 6), legend.title = element_text(size = 6),
          legend.key.width = unit(3,"mm"), legend.key.height = unit(2, "mm"))

@@

ggsave(
    filename = "pca_trilema.png", path = "figures/", device = "png",
    width = 3, height = 3, dpi = 300, bg = "white",
    plot = pc1
)

@@

```{r fig.height=3,fig.width=3}
a1 <- df_dat |> 
    as_tibble() |> 
    group_by(country) |> 
    dplyr::summarize(
        EF = sum(d_EF, na.rm = TRUE),
        Gini = sum(d_gini, na.rm = TRUE),
        GNI = sum(d_gni, na.rm = TRUE)
    ) |> 
    mutate(Group = as.character(stab@clusterObjs$kmeans$`3`$cluster)) |> 
    left_join(
        dat |> select(country, country_code) |> 
            filter(!is.na(country_code)) |> unique()) |> 
    ggplot(aes(EF, Gini)) +
    geom_segment(
        aes(x = 0, y = 0, xend = EF, yend = Gini, color = as.factor(Group)),
        arrow = arrow(length = unit(0.1, "cm")), show.legend = FALSE, size = 0.15) +
    geom_text(
        aes(x = EF *1.1, y = Gini * 1.1, label = country_code, colour = Group), 
        size = 1, show.legend = FALSE) +
    scale_color_manual("Groups", values = c("#73B3A3","#FEA621","#5BA4CA")) +
    labs(x = "Ecological Footprint", y = "Gini") +
    theme_light(base_size = 6) +
    theme(panel.grid = element_blank(), legend.position = c(0.8,0.2), 
          legend.text = element_text(size = 4), legend.title = element_text(size =4),
          legend.key.width = unit(2,"mm"), legend.key.height = unit(2, "mm"))

@@

```{r fig.width=3, fig.height=3}
a2 <- df_dat |> 
    as_tibble() |> 
    group_by(country) |> 
    dplyr::summarize(
        EF = sum(d_EF, na.rm = TRUE),
        Gini = sum(d_gini, na.rm = TRUE),
        GNI = sum(d_gni, na.rm = TRUE)
    ) |> 
    mutate(Group = as.character(stab@clusterObjs$kmeans$`3`$cluster)) |> 
    left_join(
        dat |> select(country, country_code) |> 
            filter(!is.na(country_code)) |> unique()) |> 
    ggplot(aes(GNI, Gini)) +
    geom_segment(
        aes(x = 0, y = 0, xend = GNI, yend = Gini, 
            color = as.factor(Group)), show.legend = FALSE,
        arrow = arrow(length = unit(0.1, "cm")), size = 0.15) +
    geom_text(aes(x = GNI * 1.1, y = Gini *1.1, 
                  label = country_code, colour = Group), 
              size = 1, show.legend = FALSE) +
    scale_color_manual("Groups", values = c("#73B3A3","#FEA621","#5BA4CA")) +
    theme_light(base_size = 6) + labs(x = "GNI [log]") +
    theme(panel.grid = element_blank(), legend.position = c(0.8,0.2),
          legend.text = element_text(size = 4), legend.title = element_text(size = 4),
          legend.key.width = unit(2,"mm"), legend.key.height = unit(2, "mm"))

@@

```{r fig.height=3, fig.width=3}
a3 <- df_dat |> 
    as_tibble() |> 
    group_by(country) |> 
    dplyr::summarize(
        EF = sum(d_EF, na.rm = TRUE),
        Gini = sum(d_gini, na.rm = TRUE),
        GNI = sum(d_gni, na.rm = TRUE)
    ) |> 
    mutate(Group = as.character(stab@clusterObjs$kmeans$`3`$cluster)) |> 
    left_join(
        dat |> select(country, country_code) |> 
            filter(!is.na(country_code)) |> unique()) |> 
    ggplot(aes(GNI, EF)) +
    geom_segment(
        aes(x = 0, y = 0, xend = GNI, yend = EF, 
            color = as.factor(Group)), show.legend = FALSE, 
        arrow = arrow(length = unit(0.1, "cm")), size = 0.15) +
    geom_text(aes(x = GNI * 1.1, y = EF *1.1, 
                  label = country_code, colour = Group), 
              size = 1, show.legend = FALSE) +
    scale_color_manual("Groups", values = c("#73B3A3","#FEA621","#5BA4CA")) +
    theme_light(base_size = 6) + labs(y = "Ecological footprint") +
    theme(panel.grid = element_blank(), legend.position = c(0.8,0.8),
          legend.text = element_text(size = 4), legend.title = element_text(size = 4),
          legend.key.width = unit(2,"mm"), legend.key.height = unit(2, "mm"))

@@

df_all <- gini |> left_join(ef) |> left_join(gni)

df_all <- df_all |> ungroup() |> 
    filter(!is.na(sd_gini), !is.na(m_ef), !is.na(sd_ef), !is.na(m_gni), !is.na(sd_gni)) 
```

@@

clust_num <- NbClust::NbClust( 
    data = (df_all %>% as.data.frame() %>% 
        select(where(is.numeric)) ),
    #distance = "maximum",
    min.nc = 2, max.nc = 7, 
    method = m, 
    index = 'all')
```

@@

library(clValid)
library(mclust)
## Stability & Internal validation
stab <- clValid::clValid(
    obj = df_all %>% as.data.frame() %>% 
        select(where(is.numeric)) %>%
        as.matrix(),
    nClust = 2,
    clMethods = c(
        "hierarchical", "kmeans",  "som", 
        "model", "diana", "sota", "pam", "clara", "agnes"),
    validation = c('stability', "internal"),
    #metric = "manhattan",
    method = "ward",
    verbose = FALSE
) ## Hierarchical is the optimal method

@@

```{r}
stab@clusterObjs$pam$`2`$clustering

@@

```{r}
df_all |> 
    mutate(clus = stab@clusterObjs$pam$`2`$clustering ) 
```

```{r}
pc_all <- prcomp(df_all |> 
                 select(where(is.numeric)) ,
             center = TRUE, scale. = TRUE)

pc2 <- ggbiplot::ggbiplot(
    pc_all, groups = as.character(stab@clusterObjs$pam$`2`$clustering ),
    ellipse = TRUE, labels = df_all$country_code, labels.size = 1.5,
    varname.size = 2) +
    scale_color_manual("Groups", values = c("#73B3A3","#FEA621")) +
    labs(tag = "B") + 
    theme_light(base_size = 6) +
    theme(legend.position = c(0.2, 0.2), panel.grid = element_blank(),
          legend.text = element_text(size = 6), legend.title = element_text(size = 6),
          legend.key.width = unit(3,"mm"), legend.key.height = unit(2, "mm"))

@@

ggsave(
    filename = "pca_trilemma.png", path = "figures/", device = "png",
    width = 6, height = 3, dpi = 300, bg = "white",
    plot = pc1+pc2
)
```

@@

ef_map <-  world |>
    filter(!is.na(pop)) |> 
    left_join(ef, by = c("iso_a2" = "isoa2")) |> 
    ggplot() +
    geom_sf(aes(fill = m_ef), size = 0.05, color = "white") +
    scico::scale_fill_scico(
        "Mean Ecological Footprint",palette = "romaO",
        guide = guide_colorbar(title.position = "top")) + 
    labs(tag = "A") +
    theme_void(base_size = 6) +
    theme(legend.position = "bottom", legend.key.height = unit(2, "mm"), 
          legend.key.width = unit(8, "mm"))

gini_map <-  world |>
    filter(!is.na(pop)) |> 
    left_join(gini, by = c("iso_a2" = "isoa2")) |> 
    ggplot() +
    geom_sf(aes(fill = m_gini), size = 0.05, color = "white") +
    scico::scale_fill_scico(
        "Mean Gini",palette = "berlin",
        guide = guide_colorbar(title.position = "top")) + 
    labs(tag = "B") +
    theme_void(base_size = 6) +
    theme(legend.position = "bottom", legend.key.height = unit(2, "mm"), 
          legend.key.width = unit(8, "mm"))

gni_map <-  world |>
    left_join(gini |> dplyr::select(isoa2, country_code),  
              by = c("iso_a2" = "isoa2") ) |> 
    left_join(gni |> ungroup() |> select(-country)) |> 
    filter(!is.na(pop)) |>
    ggplot() +
    geom_sf(aes(fill = m_gni), size = 0.05, color = "white") +
    scico::scale_fill_scico(
        "Mean Gross National Income",palette = "batlowW",
        guide = guide_colorbar(title.position = "top")) + 
    labs(tag = "C") +
    theme_void(base_size = 6) +
    theme(legend.position = "bottom", legend.key.height = grid::unit(2, "mm"), 
          legend.key.width = grid::unit(8, "mm"))

ef_map + gini_map + gni_map

ggsave(
    filename = "maps_trilemma.png", path = "figures/", device = "png",
    width = 6, height = 1.5, dpi = 400, bg = "white",
    plot = ef_map + gini_map + gni_map
)

@@

>>>>

```{r}
ecofp <- list()
fls <- list.files("data/ecofootprint/")
ecofp <- purrr::map(fls, function(x) {
    jsonlite::read_json(
        path = paste0("data/ecofootprint/", x),
        simplifyVector = TRUE)
    }) %>% 
    bind_rows()

@@

# ggsave(
#     plot = p, path = "figures/", file = "first_diff.png", device = "png",
#     width = 6, height = 3, dpi = 300, bg = "white")
p + theme_light(base_size = 20)
```
```{r fig.width=3, fig.height=3}
c1 <- df_dat |> 
    ggplot(aes(EFconsPerCap, gini)) +
    geom_hline(yintercept = 30, linetype = 2, color = "gray50") +
    geom_vline(xintercept = 1.68, linetype = 2, color = "gray50") +
    geom_density2d(size = 0.25, color = "#446B9C") +
    geom_point(aes(color = gni_log), size = 0.5) +
    geom_path(aes(group = country), size = 0.1) +
    scico::scale_color_scico("Prosperity (GNI [log])") +
    labs(y = "Inequality (Gini)", x = "Ecological footprint") +
    theme_light(base_size = 6) +
    theme(legend.position = "top", panel.grid = element_blank(),
          legend.key.width = unit(7, "mm"), legend.key.height = unit(2,"mm"))

c1 + theme_light(base_size = 18)
```
```{r fig.width=3, fig.height=3}
c2 <- df_dat |> 
    ggplot(aes(gni2, gini)) +
    geom_density2d(size = 0.25, color = "#446B9C") +
    geom_point(aes(color = EFconsPerCap), size = 0.5) +
    geom_path(aes(group = country), size = 0.1) +
    geom_hline(yintercept = 30, linetype = 2, color = "gray50") +
    geom_vline(xintercept = (12546), linetype = 2, color = "gray50") +
    scico::scale_color_scico("Ecological footprint",palette = "berlin") +
    labs(x= "Prosperity (GNI [log])", y = "Inequality (Gini)") +
    scale_x_log10() +
    theme_light(base_size = 6) +
    theme(legend.position = "top", panel.grid = element_blank(),
          legend.key.width = unit(7, "mm"), legend.key.height = unit(3,"mm"))

c2 + theme_light(base_size = 7)
```
```{r fig.width=3, fig.height=3}
c3 <- df_dat |> 
    ggplot(aes(gni2, EFconsPerCap)) +
    geom_density2d(size = 0.25, color = "#446B9C") +
    geom_point(aes(color = gini), size =0.5) +
    geom_path(aes(group = country), size = 0.1) +
    scico::scale_color_scico("Inequality (Gini)") +
    labs(x = "Prosperity (GNI)", y = "Ecological footprint") +
    scale_x_log10()+
    geom_hline(yintercept = 1.68, linetype = 2, color = "gray50") +
    geom_vline(xintercept = (12546), linetype = 2, color = "gray50") +
    theme_light(base_size = 6) +
    theme(legend.position = "top", panel.grid = element_blank(),
          legend.key.width = unit(7, "mm"), legend.key.height = unit(3,"mm"))

@@

pc1 <- ggbiplot::ggbiplot(
    pc, groups = as.character(stab@clusterObjs$kmeans$`3`$cluster),
    ellipse = TRUE, labels = df_summary$country_code, labels.size = 1,
    varname.size = 1.5) +
    scale_color_manual("Groups", values = c("#73B3A3","#FEA621","#5BA4CA")) +
    labs(tag = "A") +
    theme_light(base_size = 5) +
    theme(legend.position = c(0.2, 0.2), panel.grid = element_blank(),
          legend.text = element_text(size = 5), legend.title = element_text(size = 5),
          legend.key.width = unit(3,"mm"), legend.key.height = unit(2, "mm"))

@@

# ggsave(
#     filename = "pca_trilema.png", path = "figures/", device = "png",
#     width = 3, height = 3, dpi = 300, bg = "white",
#     plot = pc1
# )

@@

```{r fig.height=3,fig.width=3}
a1 <- df_dat |> 
    as_tibble() |> 
    group_by(country) |> 
    dplyr::summarize(
        EF = sum(d_EF, na.rm = TRUE),
        Gini = sum(d_gini, na.rm = TRUE),
        GNI = sum(d_gni, na.rm = TRUE)
    ) |> 
    mutate(Group = as.character(stab@clusterObjs$kmeans$`3`$cluster)) |> 
    left_join(
        dat |> select(country, country_code) |> 
            filter(!is.na(country_code)) |> unique()) |> 
    ggplot(aes(EF, Gini)) +
    geom_segment(
        aes(x = 0, y = 0, xend = EF, yend = Gini, color = as.factor(Group)),
        arrow = arrow(length = unit(0.1, "cm")), show.legend = FALSE, size = 0.15) +
    geom_text(
        aes(x = EF *1.1, y = Gini * 1.1, label = country_code, colour = Group), 
        size = 1, show.legend = FALSE) +
    scale_color_manual("Groups", values = c("#73B3A3","#FEA621","#5BA4CA")) +
    labs(x = "Ecological Footprint", y = "Inequality (Gini)") +
    theme_light(base_size = 6) +
    theme(panel.grid = element_blank(), legend.position = c(0.8,0.2), 
          legend.text = element_text(size = 4), legend.title = element_text(size =4),
          legend.key.width = unit(2,"mm"), legend.key.height = unit(2, "mm"))

@@

```{r fig.width=3, fig.height=3}
a2 <- df_dat |> 
    as_tibble() |> 
    group_by(country) |> 
    dplyr::summarize(
        EF = sum(d_EF, na.rm = TRUE),
        Gini = sum(d_gini, na.rm = TRUE),
        GNI = sum(d_gni, na.rm = TRUE)
    ) |> 
    mutate(Group = as.character(stab@clusterObjs$kmeans$`3`$cluster)) |> 
    left_join(
        dat |> select(country, country_code) |> 
            filter(!is.na(country_code)) |> unique()) |> 
    ggplot(aes(GNI, Gini)) +
    geom_segment(
        aes(x = 0, y = 0, xend = GNI, yend = Gini, 
            color = as.factor(Group)), show.legend = FALSE,
        arrow = arrow(length = unit(0.1, "cm")), size = 0.15) +
    geom_text(aes(x = GNI * 1.1, y = Gini *1.1, 
                  label = country_code, colour = Group), 
              size = 1, show.legend = FALSE) +
    scale_color_manual("Groups", values = c("#73B3A3","#FEA621","#5BA4CA")) +
    theme_light(base_size = 6) + labs(x = "Prosperity (GNI [log])", y = "Inequality (Gini)") +
    theme(panel.grid = element_blank(), legend.position = c(0.8,0.2),
          legend.text = element_text(size = 4), legend.title = element_text(size = 4),
          legend.key.width = unit(2,"mm"), legend.key.height = unit(2, "mm"))

@@

```{r fig.height=3, fig.width=3}
a3 <- df_dat |> 
    as_tibble() |> 
    group_by(country) |> 
    dplyr::summarize(
        EF = sum(d_EF, na.rm = TRUE),
        Gini = sum(d_gini, na.rm = TRUE),
        GNI = sum(d_gni, na.rm = TRUE)
    ) |> 
    mutate(Group = as.character(stab@clusterObjs$kmeans$`3`$cluster)) |> 
    left_join(
        dat |> select(country, country_code) |> 
            filter(!is.na(country_code)) |> unique()) |> 
    ggplot(aes(GNI, EF)) +
    geom_segment(
        aes(x = 0, y = 0, xend = GNI, yend = EF, 
            color = as.factor(Group)), show.legend = FALSE, 
        arrow = arrow(length = unit(0.1, "cm")), size = 0.15) +
    geom_text(aes(x = GNI * 1.1, y = EF *1.1, 
                  label = country_code, colour = Group), 
              size = 1, show.legend = FALSE) +
    scale_color_manual("Groups", values = c("#73B3A3","#FEA621","#5BA4CA")) +
    theme_light(base_size = 6) + labs(y = "Ecological footprint", x = "Prosperity (GNI)") +
    theme(panel.grid = element_blank(), legend.position = c(0.8,0.8),
          legend.text = element_text(size = 4), legend.title = element_text(size = 4),
          legend.key.width = unit(2,"mm"), legend.key.height = unit(2, "mm"))

@@

df_all2 <- gini |> left_join(ef) |> left_join(gni)

df_all2 <- df_all |> ungroup() |> 
    filter(!is.na(sd_gini), !is.na(m_ef), !is.na(sd_ef), !is.na(m_gni), !is.na(sd_gni)) 
```

@@

clust_num2 <- NbClust::NbClust( 
    data = (df_all2 %>% as.data.frame() %>% 
        select(where(is.numeric)) ),
    #distance = "maximum",
    min.nc = 2, max.nc = 7, 
    method = m, 
    index = 'all')
```

@@

library(clValid)
library(mclust)
## Stability & Internal validation
stab2 <- clValid::clValid(
    obj = df_all2 %>% as.data.frame() %>% 
        select(where(is.numeric)) %>%
        as.matrix(),
    nClust = 2,
    clMethods = c(
        "hierarchical", "kmeans",  "som", 
        "model", "diana", "sota", "pam", "clara", "agnes"),
    validation = c('stability', "internal"),
    #metric = "manhattan",
    method = "ward",
    verbose = FALSE
) ## Hierarchical is the optimal method

@@

```{r}
stab2@clusterObjs$pam$`2`$clustering

@@

```{r}
df_all2 |> 
    mutate(clus = stab2@clusterObjs$pam$`2`$clustering ) 
```

```{r}
pc_all <- prcomp(df_all2 |> 
                 select(where(is.numeric)) ,
             center = TRUE, scale. = TRUE)

pc2 <- ggbiplot::ggbiplot(
    pc_all, groups = as.character(stab2@clusterObjs$pam$`2`$clustering ),
    ellipse = TRUE, labels = df_all2$country_code, labels.size = 1,
    varname.size = 1.5) +
    scale_color_manual("Groups", values = c("#73B3A3","#FEA621")) +
    labs(tag = "B") + 
    theme_light(base_size = 5) +
    theme(legend.position = c(0.2, 0.2), panel.grid = element_blank(),
          legend.text = element_text(size = 5), legend.title = element_text(size = 5),
          legend.key.width = unit(3,"mm"), legend.key.height = unit(2, "mm"))

@@

# ggsave(
#     filename = "pca_trilemma.png", path = "figures/", device = "png",
#     width = 6, height = 3, dpi = 300, bg = "white",
#     plot = pc1+pc2
# )
```

@@

ef_map <-  world |>
    filter(!is.na(pop)) |> 
    left_join(ef, by = c("iso_a2" = "isoa2")) |> 
    ggplot() +
    geom_sf(aes(fill = m_ef), size = 0.05, color = "white") +
    scico::scale_fill_scico(
        "Mean Ecological Footprint",palette = "romaO",
        guide = guide_colorbar(title.position = "top")) + 
    labs(tag = "C") +
    theme_void(base_size = 5) +
    theme(legend.position = "bottom", legend.key.height = unit(1, "mm"), 
          legend.key.width = unit(5, "mm"))

gini_map <-  world |>
    filter(!is.na(pop)) |> 
    left_join(gini, by = c("iso_a2" = "isoa2")) |> 
    ggplot() +
    geom_sf(aes(fill = m_gini), size = 0.05, color = "white") +
    scico::scale_fill_scico(
        "Mean Gini",palette = "berlin",
        guide = guide_colorbar(title.position = "top")) + 
    labs(tag = "D") +
    theme_void(base_size = 5) +
    theme(legend.position = "bottom", legend.key.height = unit(1, "mm"), 
          legend.key.width = unit(5, "mm"))

gni_map <-  world |>
    left_join(gini |> dplyr::select(isoa2, country_code),  
              by = c("iso_a2" = "isoa2") ) |> 
    left_join(gni |> ungroup() |> select(-country)) |> 
    filter(!is.na(pop)) |>
    ggplot() +
    geom_sf(aes(fill = m_gni), size = 0.05, color = "white") +
    scico::scale_fill_scico(
        "Mean Gross National Income",palette = "batlowW",
        guide = guide_colorbar(title.position = "top")) + 
    labs(tag = "E") +
    theme_void(base_size = 5) +
    theme(legend.position = "bottom", legend.key.height = grid::unit(1, "mm"), 
          legend.key.width = grid::unit(5, "mm"))

ef_map + gini_map + gni_map
# 
# ggsave(
#     filename = "maps_trilemma.png", path = "figures/", device = "png",
#     width = 6, height = 1.5, dpi = 400, bg = "white",
#     plot = ef_map + gini_map + gni_map
# )

@@

ggsave(
    filename = "pca_maps.png", path = "figures/", device = "png",
    width = 5, height = 4, dpi = 400, bg = "white",
    plot = (pc1 / pc2 ) | (ef_map / gini_map / gni_map) + 
    plot_annotation(tag_levels = "A") + 
    plot_layout(widths = c(1,4), tag_level = "new")
)
